A Large-Scale Study of the Use of Eval in R

### 2020-11-02 inst/paper/main.tex
Fix R syntax highlighting

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}
\lstdefinestyle{R}{ %
  language=R,
  deletekeywords={new, env, equal, c, runif, trace, args, exp, t, all, get,
    names, is, environment, class, substitute, expression, list, null, Internal,
    sample, diag, length, rep, nrow, stop, offset, pmax, Machine,
    double, parent, frame, par, methods, end, dir, apply, deparse, missing,
    plot, as, integer, character, inherits, numeric, paste, eval, quote, call,
    formula, df, log, sum, c, local, legend, file, scale, round, title, order,
    drop, which, grid, print, ncol, dim, max, format, sort, rug, matrix, start,
    unique, mean, df, attr, do, power},
  otherkeywords={},
  breaklines=true
}

>>>>

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}
\lstdefinestyle{R}{ %
  language=R,
  deletekeywords={new, env, equal, c, runif, trace, args, exp, t, all, get,
    names, is, environment, class, substitute, expression, list, null, Internal,
    sample, diag, length, rep, nrow, stop, offset, pmax, Machine,
    double, parent, frame, par, methods, end, dir, apply, deparse, missing,
    plot, as, integer, character, inherits, numeric, paste, eval, quote, call,
    formula, df, log, sum, c, local, legend, file, scale, round, title, order,
    drop, which, grid, print, ncol, dim, max, format, sort, rug, matrix, start,
    unique, mean, df, attr, do, power, \$},
  otherkeywords={},
  breaklines=true
}
